gtsummary

### 2020-12-18 rmarkdown-gtsummary.Rmd
updates

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidemce interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
) %>%
  gt(caption = "`tbl_summary()` functions to add information") %>%
  fmt_markdown(everything()) %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl\\_summary()} functions to add information}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_family.tex")
```

>>>>

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidence interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
) %>%
  gt(caption = "`tbl_summary()` functions to add information") %>%
  fmt_markdown(everything()) %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl\\_summary()} functions to add information}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_family.tex")
```

### 2020-12-18 tbl_tbl_summary_family.tex
in progress
updates

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{ll}
\caption{\label{tab:}\texttt{tbl_summary()} functions to add information}\\
\toprule
Function & Description \\ 
\midrule
\texttt{add\_p()} & add p-values to the output comparing values across groups \\ 
\texttt{add\_overall()} & add a column with overall summary statistics \\ 
\texttt{add\_n()} & add a column with N (or N missing) for each variable \\ 
\texttt{add\_difference()} & add column for difference between two group, confidemce interval, and p-value \\ 
\texttt{add\_stat\_label()} & add label for the summary statistics shown in each row \\ 
\texttt{add\_stat()} & generic function to add a column with user-defined values \\ 
\texttt{add\_q()} & add a column of q values to control for multiple comparisons \\ 
\bottomrule
\end{longtable}

>>>>

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{ll}
\caption{\label{tab:}\texttt{tbl\_summary()} functions to add information}\\
\toprule
Function & Description \\ 
\midrule
\texttt{add\_p()} & add p-values to the output comparing values across groups \\ 
\texttt{add\_overall()} & add a column with overall summary statistics \\ 
\texttt{add\_n()} & add a column with N (or N missing) for each variable \\ 
\texttt{add\_difference()} & add column for difference between two group, confidence interval, and p-value \\ 
\texttt{add\_stat\_label()} & add label for the summary statistics shown in each row \\ 
\texttt{add\_stat()} & generic function to add a column with user-defined values \\ 
\texttt{add\_q()} & add a column of q values to control for multiple comparisons \\ 
\bottomrule
\end{longtable}
